Carryover effects in free recall reveal how prior experiences influence memories of new experiences

### 2023-01-12 paper/main.tex
working on results section-- writing up order manipulation results (early lists)

>>>>

Across six order manipulation conditions, we sorted early lists by each feature
dimension but randomly ordered the items on late lists (see \textit{Order
manipulation conditions}; features: category, size, length, first letter,
color, and location). Participants in the category-ordered condition showed an
increase in memory performance on early lists (accuracy, relative to early
feature rich lists; $t(95) = 3.034, p = 0.003$). Participants in the
color-ordered condition also showed a trending increase in memory performance
on early lists (again, relative to early feature rich lists: $t(96) = 1.850, p
= 0.067$). Participants' performance on early lists in all of the other order
manipulation conditions was indistinguishable from performnace on the early
feature rich lists ($\|t\|$s $< 1.013, p$s $> 0.314$). Participants in both of
the semanticly ordered conditions exhibited stronger temporal clustering on
early lists (versus early feature rich lists; category: $t(95) = 8.508, p <
0.001$; size: $t(95) = 2.429, p = 0.017$). Participants in the length-ordered
condition tended to exhibit \textit{less} temporal clustering on early lists
relative to early feature rich lists ($t(95) = -1.666, p = 0.099$), whereas
participants in the first letter-ordered condition exhibited stronger temporal
clustering on early lists ($t(95) = 2.587, p = 0.011$). Participants in the
visually ordered conditions exhibited more similar performance on early lists,
relative to early feature rich lists (color: $t(96) = -1.064, p = 0.290$; we
found a trending enhancement for participants in the location-ordered
condition: $t(95) = 1.682, p = 0.096$). We also compared feature-based
clustering on early lists across the order manipulation and feature rich
conditions. Since results were similar across both semantic conditoins
(category and size), both lexicographic conditions (length and first letter),
and both visual conditions (color and location), here we aggregate data from
conditions that manipulated each of these three feature groupings in our
comparisons to simplify the presentation. On early lists, participants in the
semantically ordered conditions exhibited stronger semantic clustering relative
to participants in the feature rich condition (category: $t(125) = 2.524, p =
0.013$; size:$t(125) = 3.510, p = 0.001$), but showed no reliable differences
in lexicographic (length: $t(125) = 0.539, p = 0.591$; first letter: $t(125) =
-0.587, p = 0.558$) or visual (color: $t(125) = -0.579, p = 0.564$; location:
$t(125) = -0.346, p = 0.730$) clustering. Similarly, participants in the
lexicographically ordered conditions exhibited stronger (relative to feature
rich participants) lexicographic clustering (length: $t(125) = 3.426, p =
0.001$; first letter: $t(125) = 3.236, p = 0.002$) on early lists, but showed
no reliable differences in semantic (category: $t(125) = -1.078, p = 0.283$;
size: $t(125) = -0.310, p = 0.757$) or visual (color: $t(125) = -0.209, p =
0.835$; location: $t(125) = -0.004, p = 0.997$) clustering. And participants in
the visually ordered conditions exhibited stronger visual clustering (again,
relative to feature rich participants, and on early lists; color: $t(126) =
2.099, p = 0.038$; location: $t(126) = 4.392, p = 0.000$), but showed now
reliable differences in semantic (category: $t(126) = 0.204, p = 0.839$; size:
$t(126) = -0.093, p = 0.926$) or lexicographic (length: $t(126) = 0.714, p =
0.476$; first letter: $t(126) = 0.820, p = 0.414$) clustering. Taken together,
these order manipulation results suggest several broad patterns. First, most of
the order manipulations we carried out did \textit{not} reliably affect overall
recall performance. Second, most of the order manipulations increased
participants' tendencies to temporally cluster their recalls. Third, all of the
order manipulations enhanced participants' clustering of each condition's
target feature (i.e., semantic manipulations enhanced semantic clustering,
lexicographic manipulations enhanced lexicographic clustering, and visual
manipulations enhanced visual clustering) while leaving clustering along other
feature dimensions roughly unchanged (i.e., semantic manipulations did not
affect lexicographic or color clustering, and so on).
